From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
grundstruktur der Agos eingefügt

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}

@@

\begin{equation*}
Algorthm
\end{equation*}

@@

\begin{equation*}
Algorthm
\end{equation*}

@@

\begin{equation*}
Algorthm
\end{equation*}

>>>>

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\begin{algorithm}[H]
 \caption{Algorithm for API Clustering}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
  \STATE Calculate for each API combination s1 and s2
 \STATE Accumulate the to a correlation matrix
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm for Density Based Clustering}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, maximum distance between two
neighbours in a cluster, word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE Mark s 1 and calculate the number of neighbours N in the distance ε
%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm for K-Means}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, word-vectors of the APIs
 \ENSURE  k centres
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE For each $i \in {1, ..., k}$, set the cluster Ci to be the set of points in X that are closer to $c_i$ than
they are to $c_j~for ~all ~j ~6= i$.
\STATE For each $i \in {1, . . . , k}$, set $c_i$ to be the centre of mass of all points in $C_i : c_i = 1 |C_i| P x \in C_i x$.
\STATE Repeat Steps 2 and 3 until C no longer changes % Das kann man auch als Loop schreiben

 \end{algorithmic}
 \end{algorithm}
